---
title: "R Notebook"
output: html_notebook
---

##Graphs on UK retail figures


```{r}
library(readr)
library(dplyr)

retail_sales <- read.csv("retail_data.csv", fileEncoding = "UTF-8-BOM")
retail_sales
```

```{r}
library(ggplot2)
all_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=All.retailing.excluding.automotive.fuel)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="For all retailing excluding automotive fuel", x="Month", y="Indexed Weekly Sales") 
all_retail_plot 

non_food_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Total.predominantly.non.food.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="For all retail excluding fuel and food", x="Month", y="Indexed Weekly Sales") 
non_food_retail_plot

textile_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Textile..clothing.and.footwear.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Textile, clothing and footwear stores", x="Month", y="Indexed Weekly Sales") 
textile_retail_plot

non_specialised_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Non.specialised.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Non-specialised stores, e.g., department stores", x="Month", y="Indexed Weekly Sales") 
non_specialised_retail_plot 

household_goods_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Household.goods.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Household goods stores", x="Month", y="Indexed Weekly Sales") 
household_goods_retail_plot
```
```{r}
# Melting table for easier graphing purposes
library(dplyr)
library(reshape2)
combined_retail_table <- melt(data=retail_sales, id.vars=c("month"), measure.vars=c("Total.predominantly.non.food.stores", "Textile..clothing.and.footwear.stores", "Household.goods.stores", "Non.specialised.stores"))
  
combined_retail_table

```

``` {r}

combined_retail_plot <- ggplot(data=combined_retail_table, aes(x=month, y=value, color=variable)) +
  geom_line() +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", x="Month", y="Indexed Weekly Sales\n(100 = 2016 sales)") +
  scale_color_discrete(name  ="Type of Store",
                       breaks = c("Total.predominantly.non.food.stores", "Textile..clothing.and.footwear.stores",
                                  "Household.goods.stores", "Non.specialised.stores"),
                       labels = c("Total predominantly non-food stores",
                                  "Textile, clothing and footwear stores",
                                  "Household goods stores",
                                  "Non-specialised stores (e.g., department stores)")
                          )
combined_retail_plot

ggsave("combined_retail_plot.png")
 

```

```{r}
library(tidyverse)

uk_cases <- read_csv("data_2020-Sep-16.csv")
#head(uk_cases)
total_cases <- uk_cases %>%
  filter(areaName == "England") %>%
  group_by(date) %>%
  map_df(rev)

total_cases <- total_cases %>%
  mutate(day=c(1:nrow(total_cases)))



total_cases <- total_cases %>%
  as.data.frame()

head(total_cases)

```
```{r}

combined_retail_plot <- ggplot(data=combined_retail_table, aes(x=month, y=value, color=variable)) +
  geom_line() +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August", "September", "October")) +
  labs(title="Indexed Weekly Sales by Month", x="Month", y="Indexed Weekly Sales\n(100 = 2016 sales)") +
  scale_color_discrete(name  ="Type of Store",
                       breaks = c("Total.predominantly.non.food.stores", "Textile..clothing.and.footwear.stores",
                                  "Household.goods.stores", "Non.specialised.stores"),
                       labels = c("Total predominantly non-food stores",
                                  "Textile, clothing and footwear stores",
                                  "Household goods stores",
                                  "Non-specialised stores (e.g., department stores)")
                          ) +
  scale_y_continuous(
    name = "Indexed Weekly Sales\n(100 = 2016 sales)",
    sec.axis = sec_axis(trans=~.*3000, name="Uh oh")
  ) +
  geom_line(data=total_cases, aes(x=month, y=cumCasesBySpecimenDate/3000, color=F))
combined_retail_plot

ggsave("retail_and_coronavirus_combined.png")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
