---
title: "R Notebook"
output: html_notebook
---

##Graphs on UK retail figures


```{r}
library(readr)
library(dplyr)

retail_sales <- read.csv("retail_data.csv", fileEncoding = "UTF-8-BOM")
retail_sales
```

```{r}
library(ggplot2)
all_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=All.retailing.excluding.automotive.fuel)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="For all retailing excluding automotive fuel", x="Month", y="Indexed Weekly Sales") 
all_retail_plot 

non_food_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Total.predominantly.non.food.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="For all retail excluding fuel and food", x="Month", y="Indexed Weekly Sales") 
non_food_retail_plot

textile_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Textile..clothing.and.footwear.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Textile, clothing and footwear stores", x="Month", y="Indexed Weekly Sales") 
textile_retail_plot

non_specialised_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Non.specialised.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Non-specialised stores, e.g., department stores", x="Month", y="Indexed Weekly Sales") 
non_specialised_retail_plot 

household_goods_retail_plot <- ggplot(data=retail_sales, aes(x=month, y=Household.goods.stores)) +
  geom_point(color="red") +
  geom_line(color="red") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", subtitle="Household goods stores", x="Month", y="Indexed Weekly Sales") 
household_goods_retail_plot 


```

``` {r}
combined_retail_plot <- ggplot(data=retail_sales, aes(x=month)) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8), labels=c("Jan", "Feb", "March", "April", "May", "June", "July", "August")) +
  labs(title="Indexed Weekly Sales by Month", x="Month", y="Indexed Weekly Sales") +
  # Non-food
  geom_point(aes(y=Total.predominantly.non.food.stores), color="red") +
  geom_line(aes(y=Total.predominantly.non.food.stores), color="red") +
  # Textiles
  geom_point(aes(y=Textile..clothing.and.footwear.stores), color="blue") +
  geom_line(aes(y=Textile..clothing.and.footwear.stores), color="blue") +
  # Household goods
  geom_point(aes(y=Household.goods.stores), color="green") +
  geom_line(aes(y=Household.goods.stores), color="green") +
  # Non-specialised
  geom_point(aes(y=Non.specialised.stores), color="orange") +
  geom_line(aes(y=Non.specialised.stores), color="orange")
combined_retail_plot

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
